
%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}


%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Divit Rawal} \\ \vspace{1pt}
    \small (425)-309-0699 $|$ \href{mailto:divit.rawal@gmail.com}{\underline{divit.rawal@gmail.com}} $|$ 
    \href{https://www.divitrawal.com}{\underline{divitrawal.com}} $|$
    \href{https://www.github.com/divitr/}{\underline{github.com/divitr}}
\end{center}

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of California, Berkeley}{Aug. 2023 -- Present}
      {Physics, Intended Computer Science}{Berkeley, CA}
      \resumeItemListStart
        \resumeItem{Relevant Coursework: Data Structures, Advanced Programming in R, Computer Programs, Communication Networks,  Information Devices and Systems, PCB Engineering}
        \resumeItem{Hands-On PCB Engineering Course Staff (Spring 2024)}
        \resumeItem{2023 National Merit Scholarship Finalist (awarded to \textless 1\% of students)}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

  \resumeSubHeadingListStart
    \resumeSubheading
      {IBM Professional Certification in Machine Learning}{Jan. 2023 -- Jun. 2023}
      {Certification}{Remote}
      \resumeItemListStart
        \resumeItem{Studied the fundamentals of machine learning including regression, clustering, classification, deep learning, and reinforcement learning}
        \resumeItem{Completed capstone project using machine learning to build recommender systems}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Amazon}{Aug. 2023 -- Dec. 2023}
      {OpenSearch Contributor}{Remote}
      \resumeItemListStart
        \resumeItem{Selected as member of 2023 OpenSearch Contributor Initiative (\textless 4\% acceptance rate)}
        \resumeItem{Contributed to the \href{https://github.com/opensearch-project/ml-commons/}{\underline{opensearch-project/ml-commons}} GitHub repository by developing machine learning algorithms, unit tests, and plugins in Java}
        \resumeItem{Collaborated with undergraduate students, graduate students, and industry professionals across the globe under the mentorship of Machine Learning Engineers at Amazon}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

  \resumeSubHeadingListStart
    \resumeSubheading
      {UC Irvine, Department of Physics \& Astronomy}{Feb. 2022 -- Jul. 2023}
      {Researcher}{Irvine, CA}
      \resumeItemListStart
        \resumeItem{Developed, trained, and tested TensorFlow/Keras deep learning models to address data scarcity issues in high momentum collision analysis with \textgreater 90\% accuracy}
        \resumeItem{Simulated particle collisions using MadGraph, Pythia8, Delphes, and ROOT and wrote reconstruction algorithms in C++ and Python to predict particle mass with \textless 2\% error}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
  \resumeSubHeadingListStart
    \resumeProjectHeading
      {\textbf{Physics Directed Reading Program} $|$ \emph{Statistical Modeling, Machine Learning}}{Aug. 2023 -- Dec. 2023}
      \resumeItemListStart
        \resumeItem{Studied applications of statistical and thermal physics to machine learning}
        \resumeItem{Investigated statistical and machine learning methods used in physics, with a focus on Markov Chain Monte Carlo simulations}
        \resumeItem{Delivered engaging presentation about the intersection of physics and machine learning to undergraduate and graduate physics students}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

  \resumeSubHeadingListStart
    \resumeProjectHeading
      {\textbf{Research-Engine} $|$ \emph{Python, Flask, Svelte, Web Scraping, Natural Language Processing}}{Nov. 2022 -- Apr. 2023}
      \resumeItemListStart
        \resumeItem{Led a team of 3 to develop Research-Engine, a tool to help users efficiently find and access relevant information and research about a topic}
        \resumeItem{Developed a full-stack web application hosted on an AWS EC2 instance using Flask and Svelte}
        \resumeItem{Implemented web scraping and natural language processing to obtain and summarize information from Google}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

  \resumeSubHeadingListStart
    \resumeProjectHeading
      {\textbf{Watersort Solver} $|$ \emph{Flutter SDK, Dart, Java}}{Jul. 2022 -- Nov. 2022}
      \resumeItemListStart
        \resumeItem{Designed and developed Watersort Solver in Java and Flutter to quickly and accurately solve any watersort brainteaser}
        \resumeItem{Published to Google Play Store}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Technical Skills}
   \begin{itemize}[leftmargin=0.15in, label={}] 
    \small{\item{
      \textbf{Languages}: Python, R, C++, Java, HTML/CSS, JavaScript, SQL\\
      \textbf{Frameworks}: ROOT, Flutter, Flask, TensorFlow/Keras, PyTorch, Mockito\\
      \textbf{Libraries}: Pandas, NumPy, Matplotlib, SciKit-Learn, BeautifulSoup
       }}
\end{itemize}

\end{document}