%-------------------------
% Cover Letter in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------------------------
%%%%%%  COVER LETTER STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{center}
    \textbf{\Huge \scshape Divit Rawal} \\ \vspace{1pt}
    \small (425)-309-0699 $|$ \href{mailto:divit.rawal@gmail.com}{\underline{divit.rawal@gmail.com}} $|$ 
    \href{https://www.divitrawal.com}{\underline{divitrawal.com}} $|$
    \href{https://www.github.com/divitr/}{\underline{github.com/divitr}}
\end{center}

\vspace{10mm}

Dear Hiring Manager,\\
\vspace{5mm}
I am writing to express my enthusiastic interest in the Physical Sciences Internship at Los Alamos National Laboratory (LANL). As an institution renowned for its cutting-edge research and contributions to the field of physics, LANL offers a unique opportunity for me to further develop my skills and knowledge in this dynamic field.\\
\vspace{5mm}
I am a freshman at UC Berkeley, pursuing a degree in Physics and Mathematics, and I am deeply passionate about the intersection of physics and computational science. I believe that my academic background and practical experience make me a strong candidate for this internship.\\
\vspace{5mm}
My previous research experience and proficiency in computational methods have prepared me well for this role. While working as a researcher in Dr. Daniel Whiteson's lab at UC Irvine, I focused on developing deep learning techniques to address data scarcity challenges in high-momentum collisions and analyzed complex data from particle collisions. Collaborating with postdoctoral researchers, I honed my data analysis skills, becoming adept at extracting meaningful insights from intricate datasets. This experience enhanced my ability to clean noisy data effectively, ensuring accurate trend extraction. Additionally, I gained valuable insights into research methodologies.\\
\vspace{5mm}
I have also completed the IBM Professional Certification in Machine Learning, where I acquired a solid theoretical foundation in data analysis and machine learning algorithms. I put this knowledge into practice in a deep-learning-based recommender system capstone project, using real-world datasets and mastering tools like Pandas, NumPy, and SciKit-Learn.\\
\vspace{5mm}
During my most recent role with Amazon, I had the privilege of being selected as one of 240 global contributors to the OpenSearch Project, an open-source initiative for real-time data storage, access, and analysis. Under the guidance of Amazon Data Engineers, I wrote unit tests and developed machine learning algorithms with far-reaching impact, serving millions of users worldwide.\\
\vspace{5mm}
I am a highly motivated and results-driven individual with a strong dedication to physics and data analysis. My enthusiasm for delving into the intricacies of physics aligns perfectly with the opportunity offered by LANL. I am excited about the chance to work with the innovative minds at LANL and contribute to advancements in the field. I am eager to apply my skills to complex challenges and push the boundaries of physics.\\
\vspace{5mm}
Thank you for considering my application. I look forward to the possibility of contributing to LANL's groundbreaking work and advancing the field of physics.\\
\vspace{5mm}
Sincerely,\\
Divit Rawal
\end{document}
